### 2018-12-04 Sections/optical_routers.tex
Reprocessed bib, remove dups
indexing

We will use the terminology that:
\begin{itemize}
	\item \textit{Ports}\index{Ports}: number of input and output optical modes in a device.
	\item \textit{Channels}\index{Channels}: number of simultaneous communications streams running in parallel through the device.
	\item \textit{Optical depth}\index{Optical!Depth}: number of primitive optical elements/devices an optical path traverses through the course of its trajectory from input to output.
	\item \textit{Directionality}\index{Directionality}: whether information is transferred in one (unidirectional) or two (bidirectional) directions.
	\item \textit{Switching time}\index{Switching time}: time for the switch to be reconfigured from one state to another.
	\item \textit{Delay time}\index{Delay time}: time taken by signal to reach the output line of the switch from input.
	\item \textit{Throughput}\index{Throughput}: maximum data rate that can flow through the switch.
	\item \textit{Switching energy}\index{Switching energy}: energy input required for activating and deactivating the switch.
	\item \textit{Power dissipation}\index{Power dissipation}: power dissipated during the process of switching.
	\item \textit{Insertion loss}\index{Insertion loss}: loss in signal power when the switch is connected.
	\item \textit{Crosstalk}\index{Crosstalk}: coupling to other optical modes.
\end{itemize}

@@

\subsection{Interferometric switches} \index{Interferometric switches}

@@

Electro-optics modulators (EOMs) are based on anisotropic materials\index{Anisotropic materials}, in which the refractive index\index{Refractive index} changes according to an applied electric field. There are two primary variations on this:
\begin{itemize}
	\item Pockel's effect\index{Pockel's effect}: a linear electro-optic effect, where the refractive index\index{Refractive index} change is proportional to the applied electric field.
	\item Kerr's effect\index{Kerr's effect}: a quadratic electro-optic effect, where the refractive index change is proportional to the square of the applied electric field.
\end{itemize}

@@

In a centrosymmetric material or Kerr's medium\index{Kerr's medium} this relation becomes (again after approximating and simplifying),
\begin{align}
n(E) = n-\frac{1}{2}\xi n^3 E^2,
\end{align}
where $\xi$ is the Kerr's coefficient\index{Kerr's coefficient} or the quadratic electro-optic coefficient. Typical values of $\xi$ lies in the range $10^{-18}-10^{-14}$m$^2$V$^{-2}$.

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{pockels_medium} \if 2\pubmode \\ \fi
\includegraphics[clip=true, width=0.475\textwidth]{kerrs_medium}
\captionspacefig \caption{Dependence of refractive index on electric field in: Pockel's medium\index{Pockel's medium}, exhibiting linear electric field dependence; Kerr's medium\index{Kerr's medium}, exhibiting quadratic electric field dependence. Graphs express qualitative behaviour only, hence no numbers are provided.}\label{fig:EOM_ref_index}
\end{figure}

@@

Sound, or acoustic waves\index{Acoustic waves}, are vibrations that travel through a medium with a velocity characteristic of the medium. This can create perturbations in the refractive index of the optical medium, thus modifying the velocity of light passing through the medium. Thus sound can be used to modify the effect of the medium on light. That is, sound can control the direction of propagation of light. This acousto-optic effect is used to make a variety of devices like optical modulators, switches, deflectors\index{Deflectors}, filters\index{Filters}, isolators\index{Isolators}, frequency shifters\index{Frequency shifters} and spectrum analysers\index{Spectrum analysers}. This is shown in Fig.~\ref{fig:AOM}.

>>>>

There are many parameters of interest characterising the operation of optical routes. We will introduce the terminology convention that:
\begin{itemize}
	\item \textit{Ports}\index{Ports}: number of input and output optical modes in a device.
	\item \textit{Channels}\index{Channels}: number of simultaneous communications streams running in parallel through the device.
	\item \textit{Optical depth}\index{Optical!Depth}: number of primitive optical elements/devices an optical path traverses through the course of its trajectory from input to output.
	\item \textit{Directionality}\index{Directionality}: whether information is transferred in one (unidirectional) or two (bidirectional) directions.
	\item \textit{Switching time}\index{Switching!Time}: time for the switch to be reconfigured from one state to another.
	\item \textit{Delay time}\index{Delay time}: time taken by signal to reach the output line of the switch from input.
	\item \textit{Throughput}\index{Throughput}: maximum data rate that can flow through the switch.
	\item \textit{Switching energy}\index{Switching!Energy}: energy input required for activating and deactivating the switch.
	\item \textit{Power dissipation}\index{Power dissipation}: power dissipated during the process of switching.
	\item \textit{Insertion loss}\index{Insertion loss}: loss in signal power when the switch is connected.
	\item \textit{Crosstalk}\index{Crosstalk}: coupling to other optical modes.
\end{itemize}

@@

\subsection{Interferometric switches} \index{Interferometric!Switches}

@@

Electro-optics modulators (EOMs) are based on anisotropic materials\index{Anisotropic materials}, in which the refractive index\index{Refractive index} changes according to an applied electric field. There are two primary variations on this:
\begin{itemize}
	\item Pockel's effect\index{Pockel's effect}: a linear electro-optic effect, where the refractive index\index{Refractive index} change is proportional to the applied electric field.
	\item Kerr's effect\index{Kerr's!Effect}: a quadratic electro-optic effect, where the refractive index change is proportional to the square of the applied electric field.
\end{itemize}

@@

In a centrosymmetric material or Kerr's medium\index{Kerr's!Medium} this relation becomes (again after approximating and simplifying),
\begin{align}
n(E) = n-\frac{1}{2}\xi n^3 E^2,
\end{align}
where $\xi$ is the Kerr's coefficient\index{Kerr's!Coefficient} or the quadratic electro-optic coefficient. Typical values of $\xi$ lies in the range $10^{-18}-10^{-14}$m$^2$V$^{-2}$.

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{pockels_medium} \if 2\pubmode \\ \fi
\includegraphics[clip=true, width=0.475\textwidth]{kerrs_medium}
\captionspacefig \caption{Dependence of refractive index on electric field in: Pockel's medium\index{Pockel's medium}, exhibiting linear electric field dependence; Kerr's medium\index{Kerr's!Medium}, exhibiting quadratic electric field dependence. Graphs express qualitative behaviour only, hence no numbers are provided.}\label{fig:EOM_ref_index}
\end{figure}

@@

Sound, or acoustic waves\index{Acoustic waves}, are vibrations that travel through a medium with a velocity characteristic of the medium. This can create perturbations in the refractive index of the optical medium, thus modifying the velocity of light passing through the medium. Thus sound can be used to modify the effect of the medium on light. That is, sound can control the direction of propagation of light. This acousto-optic effect is used to make a variety of devices like optical modulators, switches, deflectors\index{Deflectors}, filters\index{Filters}, isolators\index{Isolators}, frequency shifters\index{Frequency!Shifters} and spectrum analysers\index{Spectrum analysers}. This is shown in Fig.~\ref{fig:AOM}.

### 2018-12-04 Sections/optimising_the_world.tex
indexing

\subsubsection{Graph colouring}\index{Graph colouring}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.35\textwidth]{graph_colouring}\\
\includegraphics[clip=true, width=0.35\textwidth]{four_colouring}
\captionspacefig \caption{(top) Example of a graph with 3-colouring, such that no two vertices connected by an edge share the same colour. For this particular graph, 3-colouring is optimal (in the sense that the number of colours in minimised). It can easily be seen upon inspection that no 2-colouring is possible for this graph. Thus, this graph's chromatic number is \mbox{$\chi(G)=3$}\index{Chromatic number}. (bottom) A 4-colouring of the states of France\index{Elderberries}. Any planar map such as this has a chromatic number of at most 4 -- the `four colour theorem'.}\index{Graph colouring}\index{Surrender}\label{fig:graph_colouring}	
\end{figure}

>>>>

\subsubsection{Graph colouring}\index{Graphs!Colouring}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.35\textwidth]{graph_colouring}\\
\includegraphics[clip=true, width=0.35\textwidth]{four_colouring}
\captionspacefig \caption{(top) Example of a graph with 3-colouring, such that no two vertices connected by an edge share the same colour. For this particular graph, 3-colouring is optimal (in the sense that the number of colours in minimised). It can easily be seen upon inspection that no 2-colouring is possible for this graph. Thus, this graph's chromatic number is \mbox{$\chi(G)=3$}\index{Chromatic number}. (bottom) A 4-colouring of the states of France\index{Elderberries}. Any planar map such as this has a chromatic number of at most 4 -- the `four colour theorem'.}\index{Graphs!Colouring}\index{Surrender}\label{fig:graph_colouring}	
\end{figure}
